Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-12-06 Manuscript/manuscriptPS.tex
Update calcium density plot

    POPC:POPS (4:1)  & Berger \cite{tieleman99,mukhopadhyay04} &  0  & 0.12\footnote{Calculation of concetration complicated due the scaled ions. Concentration taken as reported in the delivered data.}   & 104:24 & 4306 & 24 & 310  & 300 & 100 & \cite{POPCpopsBERGERwith102mMCa}  \\

@@

\subsection{Ca$^{2+}$ binding affinity to bilayers with negatively charged PS lipids}
\begin{figure}[ht]
  \centering
  \includegraphics[width=9cm]{../Figs/CAdensPCPSmixture.eps}
  \caption{\label{CAdensPCPSmixture}
    Ca2+ density profiles from simulations.
  }
  \todo{The CHARMM results are mass densities, number densities should be used when the data by Jesper Madsen is available.} \\
  \todo{Should we include also counterions into the plot?} \\
  \todo{Figure needs general improvement.}
\end{figure}

>>>>

    POPC:POPS (4:1)  & Berger \cite{tieleman99,mukhopadhyay04} &  0  & 0.102\footnote{Calculation of concetration complicated due the scaled ions. Concentration taken as reported in the delivered data.}   & 104:24 & 4306 & 24 & 310  & 300 & 100 & \cite{POPCpopsBERGERwith102mMCa}  \\

@@

\subsection{Ca$^{2+}$ binding affinity to bilayers with negatively charged PS lipids}
\begin{figure}[ht]
  \centering
  \includegraphics[width=9cm]{../Figs/CAdensPCPSmixtureLOWcons.eps}
  \caption{\label{CAdensPCPSmixture}
    Ca2+ density profiles from simulations.
  }
  \todo{The CHARMM results are mass densities, number densities should be used when the data by Jesper Madsen is available.} \\
  \todo{y-axis scale of Lipid17 should be checked.} \\
  \todo{Should we include also counterions into the plot?} \\
\end{figure}

### 2018-12-06 Manuscript/manuscriptPSsuppl.tex
Update calcium density plot

>>>>

\pagebreak
\section{Calcium density profiles from simulations with POPC:POPS(5:1) mixture}
\begin{figure}[ht]
  \centering
  \includegraphics[width=9cm]{../Figs/CAdensPCPSmixture.eps}
  \caption{\label{CAdensPCPSmixtureALL}
    Ca2+ density profiles from simulations.
  }
  \todo{The CHARMM results are mass densities, number densities should be used when the data by Jesper Madsen is available.} \\
  \todo{Should we include also counterions into the plot?} \\
\end{figure}
